Reliable error estimation for Sobol' indices

### 2016-03-10 replicated_sobol.tex
added Section 3 + end of Section 1

We consider here a quasi-Monte Carlo sampling strategy to evaluate these two estimators. We focus on the estimation of all first-order Sobol' indices. The classical estimation procedure introduced by Sobol' requires to evaluate the quantity $f(\vx_u:{\vx'}_{-u})$ $n$ times for each $u \in \{1,\dots,d\}$ while the quantity $f(\vx)$ is only evaluated $n$ times once for all $u$. The total cost sums up to $n(d+1)$ evaluations of $f$. This cost can rapidly becomes prohibitive for expansive models involving an important number of parameters. An improvement to reduces this cost lies in the use of replicated designs. The notion of replicated designs was first introduced by McKay. It is defined as follows:
\begin{defin}[Replicated designs]
Let $X$ and $X'$ be two designs defined as follow:
\[\arraycolsep=1.3pt
X=\left(\begin{array}{ccccc}
x_{1,1} & ... & x_{1,j} & ... & x_{1,d} \\
\vdots &  & \vdots & & \vdots \\
x_{i,1} & ... & x_{i,j} & ... & x_{i,d} \\
\vdots &  & \vdots & & \vdots \\
x_{n,1} & ... & x_{n,j} & ... & x_{n,d} \\
\end{array} \right), \ X'=\left(\begin{array}{ccccc}
{x'}_{1,1} & ... & {x'}_{1,j} & ... & {x'}_{1,d} \\
\vdots &  & \vdots & & \vdots \\
{x'}_{i,1} & ... & {x'}_{i,j} & ... & {x'}_{i,d} \\
\vdots &  & \vdots & & \vdots \\
{x'}_{n,1} & ... & {x'}_{n,j} & ... & {x'}_{n,d} \\
\end{array} \right) 
\]
Let the symbol $X_u$ (resp. $X'_u$), $u \subsetneq \{1,\dots,d-1\}$, denotes a subset of $u$ columns of $X$ (resp. $X'$). We say that $X$ and $X'$ are two replicated designs of order $r \in \{1,\dots,d-1\}$ if:

@@

Our objective is to combine the use of Sobol' sequence with the replication method to estimate all quantities $\underline{\tau}_u^2, u \in \{1,\dots,d\}$ with only $2n$ evaluations of $f$. This translates to construct two Sobol' sequence that identify as two replicated designs of order $1$.

@@

>>>>

We consider here a quasi-Monte Carlo sampling strategy to evaluate these two estimators. We focus on the estimation of all first-order Sobol' indices. The classical estimation procedure introduced by Sobol' requires to evaluate the quantity $f(\vx_u:{\vx'}_{-u})$ $n$ times for each $u \in \{1,\dots,d\}$ while the quantity $f(\vx)$ is only evaluated $n$ times once for all $u$. The total cost sums up to $n(d+1)$ evaluations of $f$. This cost can rapidly becomes prohibitive for expansive models involving an important number of parameters. An improvement to reduces this cost lies in the use of replicated designs. The notion of replicated designs was first introduced by McKay. It is defined as follows:
\begin{defin}[Replicated designs]
Let $X$ and $X'$ be two designs defined as follow:
\[\arraycolsep=1.3pt
X=\left(\begin{array}{ccccc}
x_{1,1} & ... & x_{1,j} & ... & x_{1,d} \\
\vdots &  & \vdots & & \vdots \\
x_{i,1} & ... & x_{i,j} & ... & x_{i,d} \\
\vdots &  & \vdots & & \vdots \\
x_{n,1} & ... & x_{n,j} & ... & x_{n,d} \\
\end{array} \right), \ X'=\left(\begin{array}{ccccc}
{x'}_{1,1} & ... & {x'}_{1,j} & ... & {x'}_{1,d} \\
\vdots &  & \vdots & & \vdots \\
{x'}_{i,1} & ... & {x'}_{i,j} & ... & {x'}_{i,d} \\
\vdots &  & \vdots & & \vdots \\
{x'}_{n,1} & ... & {x'}_{n,j} & ... & {x'}_{n,d} \\
\end{array} \right).
\]
Let the symbol $X_u$ (resp. $X'_u$), $u \subsetneq \{1,\dots,d-1\}$, denotes a subset of $u$ columns of $X$ (resp. $X'$). We say that $X$ and $X'$ are two replicated designs of order $r \in \{1,\dots,d-1\}$ if:

@@

Our objective is to combine the use of Sobol' sequences with the replication method to iteratively estimate all quantities $\underline{\tau}_u^2, u \in \{1,\dots,d\}$. This would reduce the method to constructing two replicated designs of order $1$ that are iteratively augmented with new point sets. Two approaches are considered: one multiplicative and one additive. The first one uses the innate nested structure of a Sobol' sequence. The size of each replicated design is doubled at each step. The additive approach consists first of constructing a Sobol' sequence then shifting and scrambling it to form the new point sets. These new point sets are then added to the initial Sobol' sequence to form the two replicated designs. In this case, the size of each replicated design at step $k$ is $ k \times 2^m$ where $2^m$ is the size of the initial Sobol' sequence.

@@

\section{Matrix generators group $U_m$}
